Automatic Visual Inference for Linear Regression

### 2022-03-16 Milestone_presentation_1/Milestone_presentation_1/Milestone_presentation_1.Rmd
add human subject experiment

>>>>

# Human Subject Experiments

.pull-left-center[

![](images/website.png)

.caption[
Fig. 12: _Layout of the study webiste._ 
]
]

#### **Two human subject experiments** are conducted to compare humans with computer vision models on the ability of reading data plots.

#### **20** lineups are given to each participant, with **10** cubic lineups and **10** heteroskedasticity lineups across different effect sizes. **2** out of **20** lineups are extremely easy lineup which are used as attention checks. Participants need to pass at least one.

#### The same lineup will not be presented to a participant twice. Most of the lineups have been evaluated by **5** different participants.

#### Participants are allowed to **select multiple plots** from a lineup. They also need to give the **reason** and the **confidence level**.

# $p$-value and Power Estimation for Multiple Selections

#### The assumptions about the **independence** still needed. Let $K$ be the number of independent evaluations of a visual test, $s_i , i = 1, ..., K$ be the **number of selections of the evaluations**, and $X$ be the random variable denoting the number of detections. Then, the $p$-value of the visual test is given as: $$P(X\geq x) = \sum_{j=x}^{K}Pr(j|s_1,...,s_K).$$

#### The distribution of $X$ given $s_1, ...s_K$ can not be **derived trivially**, as it is a **sampling without replacement problem**. In practice, this distribution can be **approximated** by computer simulation.

# $p$-value and Power Estimation for Multiple Selections

#### Assume there is a **visual test** $V_K$, where $K$ denoting the number of evaluations. The corresponding  $p$-value of $V_K$ can be computed.

#### Meanwhile, if one evaluation is **randomly deleted** from $V_K$, the remaining evaluations can still be used to form another valid visual test $V_{K-1}$.

#### In fact, considering **all the possibilities**, $K$ different outcomes for $V_{K-1}$ can be obtained.

#### Since all outcomes occur with **equal probability**, the **proportion of outcomes which reject the null hypothesis** can be used as an **estimator of the power of the visual test** $V_{K-1}$.

#### Similarly, if we would like to estimate the power of the visual test $V_{K-j}$ given the evaluations of $V_{K}$, for $j < K$, we could find all the possible combinations of $K$ elements, taken $k-j$ at a time to obtain $K\choose{K-j}$ different outcomes for $V_{K-j}$. Then, the estimated power is given as $R/{K\choose{K-j}}$, where $R$ is the number of outcomes which reject the null hypothesis.

# Human Subject Experiment - Results

#### We collect **400** lineup evaluations made by **20** participants in experiment I and **880** lineup evaluations made by **44** participants in experiment II. In total, **442** unique lineups are evaluated by 64 subjects.

.center[![:scale 80%](images/power1.png)

.caption[
Fig. 13: _Quasibinomial GLM for estimated power for different number of evaluations._ 
]]
